\vskip-0.6in LOBBYING AND LEGISLATIVE UNCERTAINTY

### 2016-02-15 draft.tex
write prop:2NNB

\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{assumption}{Assumption}
\newtheorem{fact}{Fact}
\newtheorem{result}{Result}

@@

Vote Buyer $A$ moves first, providing a bribe offer function $a(i)$. $a(i)$ is perfectly observable to Vote Buyer $B$ when he moves second and offers bribe offer function $b(i)$. Each legislator takes these bribe offers as given and then votes for the alternative that maximizes her payoff. I assume unbribed legislators who are indifferent vote for $s$ and that all bribed legislators who are indifferent vote for whoever bribed them last.

@@

>>>>

\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{assumption}{Assumption}
\newtheorem{fact}{Fact}
\newtheorem{result}{Result}
\newtheorem{proposition}{Proposition}

@@

Vote Buyer $A$ moves first, providing a bribe offer function $a(i)$. $a(i)$ is perfectly observable to Vote Buyer $B$ when he moves second and offers bribe offer function $b(i)$. Each legislator takes these bribe offers as given and then votes for the alternative that maximizes her payoff. I assume unbribed legislators who are indifferent vote for $s$.

@@

I begin by examining the subgame that begins when Vote Buyer $B$ makes his offer. This not only serves to elucidate the basic logic of the model; it will also serve as a baseline from which to examine the incentives of Vote Buyer $A$. For now, assume that the uncertainty about each legislator's ideal point is the same.

In a legislature with three voters, Vote Buyer $B$ can choose to bribe all three legislators, two, one or none of the legislators. It is most instructive to begin with the case where he bribes two of the legislators.

\begin{proposition}
  When Vote Buyer $B$ pays bribes to exactly two legislators, the bribes are such that their ideal points net of the bribes are equalized. Which two voters are bribed depends on the bias parameter $\al$.
	\label{prop:2NNB}
\end{proposition}
